ABC Group Level Fits

### 2024-01-16 Model/abc_hier.qmd
abc indv fit visuals

walk(c("fun_alm","fun_model", "Display_Functions"), ~ source(here::here(paste0("Functions/", .x, ".R"))))
ds <- readRDS(here::here("data/e1_md_11-06-23.rds"))  |> as.data.table()
dsv <- ds |> filter(condit=="Varied")  
dsc <- ds |> filter(condit=="Constant") 
ind_ds <- ds |> 
  filter(expMode2 == "Test") |> 
  group_by(id, condit, x, expMode2) |> 
  summarise(y = mean(y), .groups = "keep")

tMax=84
avg_dsv <- ds |> filter(condit=="Varied",expMode2=="Train") |> group_by(tr) %>%
  mutate(bandInt2 = sample(rep(c(800, 1000, 1200), each = tMax / 3), tMax, replace = FALSE)[tr]) %>%
  filter(bandInt2 == x) |> select(-bandInt2) |> group_by(tr,condit,x,expMode2) |> summarise(y=mean(y),.groups="keep") |>
  rbind(dsv |> filter(expMode2=="Test") |> group_by(condit,x,expMode2) |> summarise(y=mean(y),tr=1,.groups="keep") ) |> setDT()

avg_dsc <- ds |> filter(condit=="Constant",expMode2=="Train",tr<=tMax) |> group_by(tr, condit,x,expMode2) |> 
  summarise(y=mean(y),.groups="keep") |> 
  rbind(dsc |> filter(expMode2=="Test") |> 
          group_by(condit,x,expMode2) |> 
          summarise(y=mean(y),tr=1,.groups="keep") ) |> 
  setDT()

@@

# ind_abc_s500_ng300_buf5 <- readRDS("~/Library/CloudStorage/GoogleDrive-tegorman13@gmail.com/My Drive/HTW/gl/data/indv_sim/ind_abc_s500_ng300_buf5.rds")

>>>>

walk(c("fun_alm","fun_model", "Display_Functions"), ~ source(here::here(paste0("Functions/", .x, ".R"))))
ds <- readRDS(here::here("data/e1_md_11-06-23.rds"))  |> as.data.table()
ids <- c(1,2,4,5,6,7,8, 10,11,12,13)
ids2 <- c(1,66,141,142,36,57,81)
ids3 <- c(20,71,101,4,76,192)

```{r fig.width=11, fig.height=10}
ind_fits <- readRDS("~/Library/CloudStorage/GoogleDrive-tegorman13@gmail.com/My Drive/HTW/gl/data/indv_sim/ind_abc_ss_1000_ng100_bufp55.rds")
ind_fits <- ind_fits |> list_assign(runInfo = zap())

# names(ind_fits)
# names(ind_fits$id_fits_alm_varied)
# names(ind_fits$id_fits_alm_varied[[1]])

teter_results_df <- imap_dfr(ind_fits, ~imap_dfr(.x, ~.x[["teter_results"]] ,.id="id"))

combined_results_df <- imap_dfr(ind_fits, ~imap_dfr(.x, ~{
  teter_data <- .x[["teter_results"]] %>% mutate(result_type = "teter_results")
  te_data <- .x[["te_results"]] %>% mutate(result_type = "te_results")
  tr_data <- .x[["tr_results"]] %>% mutate(result_type = "tr_results")
  combined_data <- bind_rows(teter_data, te_data, tr_data)
}, .id = "id"))

id1 <- combined_results_df |> filter(id %in% ids2) 
names(id1)
typeof(id1$sim_dat)
str(id1$sim_dat[[1]])
# sim_dat is a list dataframe. Add the value of rank into sim_dat

id1 <- id1 |> select(rank,sim_dat) |> unnest(sim_dat) |>filter(rank<=2)

```{r, fig.width=7, fig.height=6}

plt_c_gi <- combined_results_df |> 
  ggplot(aes(x=c)) + geom_density(aes(fill=Group), alpha=.5) + 
  facet_wrap(Fit_Method~Model,scales="free",ncol=2) + 
  theme_bw() + theme(legend.position = "bottom") + labs(title = "Posterior distribution of c")

plt_lr_gi <- combined_results_df |> 
  ggplot(aes(x=lr)) + geom_density(aes(fill=Group), alpha=.5) + 
  facet_wrap(Fit_Method~Model,scales="free",ncol=2) + 
  theme_bw() + theme(legend.position = "bottom") + labs(title = "Posterior distribution of lr")

plt_c_gi + plt_lr_gi

```{r fig.width=11, fig.height=18}

post_dat_long <- combined_results_df |> filter(id %in% (c(ids2,ids3)), rank<=1) |> 
  select(sim_dat) |> unnest(sim_dat) |> filter(expMode2=="Test") |>
  mutate(facet_label = paste0("Model: ", Model, "\n", "Fit: ", Fit_Method, "\n", "c: ", round(c, 4), "\n", "lr: ", round(lr, 4))) |>
  pivot_longer(cols = c(y,pred), names_to = "Resp", values_to = "val")

post_dat <- combined_results_df |> filter(id %in% (c(ids2,ids3)), rank<=5) |> 
  select(sim_dat) |> unnest(sim_dat) |> filter(expMode2=="Test")

post_dat_long |> filter(id %in% ids2) |> ggplot(aes(x = x, y = val, fill=as.factor(Model))) + 
  stat_summary(fun=mean, geom="bar", position=position_dodge(), alpha=.75) +
  stat_summary(fun.data=mean_se, geom="errorbar", position=position_dodge()) +
  #stat_halfeye(position=position_dodge()) +
  facet_wrap(~id, scales="free") + labs(title = "Average of posterior predictive distributions")

post_dat |> filter(id %in% ids2) |> ggplot(aes(x = x, y = y, fill=condit)) + 
  stat_summary(fun=mean, geom="bar", position=position_dodge(), alpha=.75) +
  stat_summary(fun.data=mean_se, geom="errorbar", position=position_dodge()) +
  stat_halfeye(aes(x=x,y=pred,color=condit),position=position_dodge()) +
  ggh4x::facet_nested_wrap(Fit_Method~Model~id, ncol=6, scales="free") + labs(title = "Average of posterior predictive distributions")

@@

post_ev <- ind_fits$id_fits_exam_varied |> 
  map_dfr(~tibble(pluck(.x$teter_results)),.id = "id") |> 
  filter(id %in% c(13)) |> 
  filter(rank==1) |> 
  select(sim_dat) |> unnest(sim_dat)

post_ev |> filter(expMode2=="Test") |> 
  ggploat(aes(x = x, y = pred, fill=condit)) + 
  stat_summary(fun=mean, geom="bar", position=position_dodge(), alpha=.75) +
  stat_summary(fun.data=mean_se, geom="errorbar", position=position_dodge()) +
  #stat_summary(fun=mean, geom="point", aes(x=x,y=y,color=condit), position=position_dodge()) +
  stat_halfeye(aes(x=x,y=y,color=condit),position=position_dodge()) +
  ggh4x::facet_nested_wrap(~id) + labs(title = "Average of posterior predictive distributions")

post_alm <- ind_fits$id_fits_alm_varied |> 
  map_dfr(~tibble(pluck(.x$teter_results)),.id = "id") |> 
  filter(id %in% c(1,2,4,5,6,7,8, 10,11,12,13)) |> 
  filter(rank<10) |> 
  select(sim_dat) |> unnest(sim_dat)

post_alm |> filter(expMode2=="Test") |> 
  ggplot(aes(x = x, y = pred, fill=condit)) + 
  stat_summary(fun=mean, geom="bar", position=position_dodge(), alpha=.75) +
  stat_summary(fun.data=mean_se, geom="errorbar", position=position_dodge()) +
  #stat_summary(fun=mean, geom="point", aes(x=x,y=y,color=condit), position=position_dodge()) +
  stat_halfeye(aes(x=x,y=y,color=condit),position=position_dodge()) +
  ggh4x::facet_nested_wrap(~id) + labs(title = "Average of posterior predictive distributions")

```{r}
#| eval: false
# ind_abc_s500_ng300_buf5 <- readRDS("~/Library/CloudStorage/GoogleDrive-tegorman13@gmail.com/My Drive/HTW/gl/data/indv_sim/ind_abc_s500_ng300_buf5.rds")
